%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


%---------------------------------------------------------
  \cvparagraph
    {I want a career at the [employer] because I want to get hands on experience with cutting edge technology, help our country stay safe, and have opportunities for future career advancement. \\}



  \cvparagraph
  {  This past summer, I interned at Sandia National Labs. There, I worked hands-on with 2 different projects, and by doing that, I learned more in those 10 weeks than in months at my high school. In tech, learning by doing is important because reading and memorizing a book isn’t the same as being able to use and apply those concepts in real life. At the [employer], I would learn about the different aspects of the vast field of computer science, and the experience in each would allow me to make a more informed decision of what I want to specialize in. In addition, the [employer], as a part of the government, has access to some of the most cutting-edge technology. This is a rare opportunity, and I would love to pioneer the software.\\}


\cvparagraph{In addition, at Sandia Labs, I also performed cybersecurity research and became more interested in it as a career. Previously, I wanted to be an app developer, but performing research in a real lab and going through the process was exhilarating. It required critical thinking skills that made me use all the information I had to come up with new conclusions, and that analysis is something I love to do. Not only is innovation interesting, but I also want to optimize existing systems. I currently do code golf to optimize programs and want to make algorithms more efficient. I also like to pentest and stress test systems, because it’s interesting to see how much they can take. In addition, I’m an avid speedcuber and puzzle solver, so logic and critical thinking come easy to me.  Research into better computer security methods is essential in order to protect US secrets, and I can help conduct that research with my various skills.\\}

\cvparagraph{Not only do I have the technical knowledge, but I also have good teamwork skills and leadership ability. In high school, I was president of my CSF club, where the officers and I organized many fundraisers, like food drives and bake sales. By getting more students involved in these events, the officers and I made our community a better place and our school’s students better people. I would like to work at the [employer], and eventually progress into a leadership role, so I can encourage others to work well, while having the technical skills necessary to help them.\\}

\cvparagraph{In addition to my technical skills and leadership ability, I’d like to give back to the government. The US is one of the best countries to grow up in, and I want to show my appreciation. As a scrawny person, I’m not a good fit for fighting in the military; my strength lies with computers. I know my skills can be put to good use in creating military technology and innovating safer weaponry for the country. \\}

\cvparagraph{Lastly, the [employer] has many opportunities for career advancements and changes. Many of the technical positions have an overlap; I can work on a variety of projects with my wide array of skills. The [employer] isn’t mundane work; it’s dynamic, depending on the needs of the nation.  With my experience as a high schooler who has worked in app programming, cybersecurity, design and graphics, and a variety of systems, I could easily work in multiple fields at the [employer], like computer science, cryptanalysis, or information assurance. By working at the [employer], and being trained there, I can become a useful and important employee from the beginning. \\}

\cvparagraph{
The [employer] is an diverse and safe place of employment that meets my objectives, and affords me rare opportunities that I cannot find elsewhere. This is why I want a career at the [employer].\\}
    
%---------------------------------------------------------

